---
title: "postal"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Installation

```
remotes::install_github("BigelowLab/postal")
```

A very simple wrapper in R around various email applications on linux (and possibly macos, too.)  Currently supports [`mail`](https://www.binarytides.com/linux-mail-command-examples/), [`mutt`](http://www.mutt.org/) and [`nail`](http://nail.sourceforge.net/).  If you don't have one of these installed then you need to install at least one.

### Usage

All of the wrappers accept standard arguments: `to`, `subject`, `message`, `attachment` and `verbose`.  The latter just prints the command that was issued whether or not it was successful.

One function, `sendmail()`, serves a one-stop shopping to access any of the the three applications; it's really the only function you need to call. Choose your mail application using the `app` argument which defaults to "mail".

```{r usage}
library(postal)
ok <- sendmail(to = c("someone@somewhere.com", "and_her_uncle@boondocks.com"),
               subject = "Ice out yet?",
               message = c("Hi,", "Has the ice on the pond melted yet?", "Love, Bubby"),
               attachment = "/path/to/a/file.pdf",
               app = "mail",
               verbose = TRUE)
```


